Biologically-Constrained Region Merging for Connectome Reconstruction

### 2018-05-24 papers/eccv2018/rebuttal/paper.tex
skeleton: allow locations close to border

\titlerunning{Biologically-Constrained Region Merging for Connectome Reconstruction}
\authorrunning{B. Matejek et al.}
\title{Biologically-Constrained Region Merging for Connectome Reconstruction}

\author{Brian Matejek, Daniel Haehn, Donglai Wei, Toufiq Parag, Hanspeter Pfister}
\institute{Harvard University, Cambridge, MA 02138, USA\\
	\email{bmatejek,haehn,donglai,paragt,pfister@seas.harvard.edu}}

@@

\begin{abstract}
% maybe better to cut to the point
%Advancements in electron microscopy image acquisition have created connectomics datasets terabytes in size making manual reconstruction of neuronal structures infeasible.
%In the past decade in Connectomics, much progress has been made to classify neural membranes or affinities from the raw pixel and to watershed transform them into initial segments.
%Current state-of-the-art automatic methods classify neural membranes or affinities from the raw pixel followed by agglomeration methods to create full neuron reconstructions.
%An agglomerative segmentation algorithm merges initial pair of clusters.
Current state-of-the-art connectome reconstruction pipelines have two major steps: initial pixel-based segmentation with affinity prediction and watershed transform, and refined segmentation by merging over-segmented regions.
For the region merging, most methods neglect geometric and topological constraints that are inherent in the graph structure of neural wiring diagrams.
In this work, we use a biologically-constrained graph-based method to better reconstruct neural pathways.
Given the initial segmentation, we first create a graph with nodes corresponding to segment labels and edges identifying potential locations of split errors based on the skeleton structure of the segmentation.
Next, we train a convolutional neural network to capture the geometric properties of segment connections and produce edge weights as the probability of merging two nodes.
Finally, we formulate the region merging as a lifted multicut partitioning problem with topological constraints to avoid cycles.
We demonstrate the performance of our approach on multiple real-world connectomics datasets with an average variation of information improvement of 8.2\%.
\keywords{connectomics, biological constraints, region merge, skeletonization, deep learning, lifted multicut}
\end{abstract}

\input{0_introduction}

\input{1_related_work}

\input{2_method}

\input{3_evaluation}

\input{4_results}

\input{5_conclusions}

\clearpage

>>>>

%\titlerunning{Biologically-Constrained Region Merging for Connectome Reconstruction}
%\authorrunning{B. Matejek et al.}
\title{Biologically-Constrained Region Merging for Connectome Reconstruction}

%\author{Brian Matejek, Daniel Haehn, Donglai Wei, Toufiq Parag, Hanspeter Pfister}
%\institute{Harvard University, Cambridge, MA 02138, USA\\
%	\email{bmatejek,haehn,donglai,paragt,pfister@seas.harvard.edu}}

@@

Hello World
